[dcpo_demsupport]

### 2020-09-30 paper/dcpo_demsupport.Rmd
finish drafting the result section; correct the CIs in the plot

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, # data wrangling
  dotwhisker, # visualization
)

@@

df_result_cls <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result),
           n = nobs(result))
})

@@

plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Institutional Democracy (Vdem)",
    subtitle = "Pooled"
  ) +
  theme(legend.position = "none")

@@

plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  theme(legend.position = "bottom")

@@

@@

df_result_clsAPSR <- map(mods, function(aMod){
  tidy(aMod) %>%
    mutate(std.error = vcovHC_se(aMod),
           n = nobs(aMod))
})

@@

df_result_dcpoMeanAPSR <- map(mods, function(aMod){
  aMod %>% 
    tidy %>%
    mutate(std.error = vcovHC_se(aMod),
           n = nobs(aMod))
})

@@

plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Democratic Mood",
    subtitle = "Basic"
  ) +
  theme(legend.position = "none")

@@

plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "w. Corruption"
  )

@@

The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in the Appendix \@ref(replicateAJPS))

>>>>

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  broom, tidyverse, # data wrangling
  dotwhisker, # visualization
)

@@

df_result_cls <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result, conf.int = TRUE) %>%
    mutate(std.error = vcovBK_se(result),
           n = nobs(result))
})

@@

plot_AJPS1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Institutional Democratization",
    subtitle = "Pooled"
  ) +
  theme(legend.position = "none")

@@

plot_AJPS2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  theme(legend.position = "bottom")

@@

The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in Appendix \@ref(replicateAJPS)).
In the pooled model (left panel), the aggregated measurement of democratic mood shows a positive effect on the institutional democratization in Claassen's original model, and the effect is statistically significant at the 0.05 level.
However, when accounting for the uncertainty of the latent variable measurement of the mood, the significance disappears.
We added one-third more data and applied a more efficient measurement (DCPO), resulting a saliently shrink of the range of measurement uncertainty, but the confidence intervals still cut zero---that is, remaining statistically insignificant.^[The point estimates also alters. We attribute it to additional more information and better measuring method by DCPO.]
Similar phenomenon also happens on the estimates of, for example, the second-time-unit lag of democratization and resouce dependency.

We further examined Claassen's regime specific model [@Claassen2019: Model 2].
The originally significant contribution of democratic mood in democratic regimes disappears as well, regardless whether more information and better method are applied.

@@

df_result_clsAPSR <- map(mods, function(aMod){
  tidy(aMod, conf.int = TRUE) %>%
    mutate(std.error = vcovHC_se(aMod),
           n = nobs(aMod))
})

@@

df_result_dcpoMeanAPSR <- map(mods, function(aMod){
  aMod %>% 
    tidy %>%
    mutate(std.error = vcovHC_se(aMod),
           n = nobs(aMod`))
})

@@

plot_APSR1 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Democratic Mood",
    subtitle = "Basic"
  ) +
  theme(legend.position = "none")

@@

plot_APSR2 <- dwplot(df_plotS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "w. Corruption"
  ) +
  theme(legend.position = "bottom")

legend <- get_legend(plot_APSR2)

@@

The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the dependent variable. 
In Figure \@ref(fig:visualizedAPSR), we examine the thermostatic model of democratic mood [@Claassen2020b]. 
The estimates without taking uncertainty into account imply that democatic mood decreases along with the progress of democratization. 
Nevertheless, this effect no longer holds when the measurement uncertainty is involved.

As previous operation, we tested if this alteration is caused by the data scarcity or estimating inefficiency. 
When more data and better method are applied, the confidence intervals do shrink yet remaining statistically insignificant. 
We observed the similar changes after adjusting the effect of domestic corruption [@Claassen2020b: 41].
